---
title: "Minnesota Lesson Logs"
output: html_notebook
---

# Preliminaries

```{r}
checkpoint::checkpoint("2021-06-10")
```

## Reading data
```{r}
lesson_logs_k <- read.csv("210606_LessonLogs_Kindergarten.csv", header = T, na.strings = c("", " "), stringsAsFactors = F, strip.white = T) %>% slice(-1:-3) 
lesson_logs_first <- read.csv("210606_LessonLogs_FirstGrade.csv", header = T, na.strings = c("", " "), stringsAsFactors = F, strip.white = T) %>% slice(-1:-3) 
lesson_logs_second <- read.csv("210606_LessonLogs_SecondGrade.csv", header = T, na.strings = c("", " "), stringsAsFactors = F, strip.white = T) %>% slice(-1:-3) 
```

## Constants & vectors

```{r}
LessonList <- c("L01", "L02", "L03", "L04", "L05", "L06", "L07", "L08", "L09", "L10", "L11", "L12", "L13", "L14", "L15", "L16", "L17", "L18", "L19", "L20", "L21", "L22", "L23", "L24")
```

## Functions

### Substrings
```{r}
right_side = function(x,n){
  substring(x,nchar(x)-n+1)
}
```


### Min, max, mean, SD

```{r}
min_max_mean_sd <- function(variable){
  
  min = round(min(variable),1)
  max = round(max(variable),1)
  mean = round(mean(variable),1)
  sd = round(sd(variable),1)
  
  my_list = list(min, max, mean, sd) 
  
  return(my_list)
}
```




## Modifying & selecting variables

```{r}
lesson_logs_k$Grade <- "Kindergarten"
lesson_logs_first$Grade <- "FirstGrade"
lesson_logs_second$Grade <- "SecondGrade"
```


```{r}
lesson_logs_k <- lesson_logs_k %>% dplyr::select(-c(Lesson1:Lesson24))
lesson_logs_first <- lesson_logs_first %>% dplyr::select(-c(Lesson1:Lesson24)) 
lesson_logs_second <- lesson_logs_second %>% dplyr::select(-c(Lesson1:Lesson24)) 
```

```{r}
lesson_logs_k <- lesson_logs_k %>% dplyr::select(-EndDate:-ResponseId) %>% dplyr::select(-RecipientFirstName:-UserLanguage)
lesson_logs_first <- lesson_logs_first %>% dplyr::select(-EndDate:-ResponseId) %>% dplyr::select(-RecipientFirstName:-UserLanguage)
lesson_logs_second <- lesson_logs_second %>% dplyr::select(-EndDate:-ResponseId) %>% dplyr::select(-RecipientFirstName:-UserLanguage)
lesson_logs_k <- lesson_logs_k %>% dplyr::select(!ends_with("Comments")) %>% dplyr::select(!contains("Files_Id")) %>% dplyr::select(!contains("Files_Type")) %>% dplyr::select(!contains("Files_Size"))  %>% dplyr::select(!contains("Files_Name"))
lesson_logs_first <- lesson_logs_first %>% dplyr::select(!ends_with("Comments")) %>% dplyr::select(!contains("Files_Id")) %>% dplyr::select(!contains("Files_Type")) %>% dplyr::select(!contains("Files_Size"))  %>% dplyr::select(!contains("Files_Name"))
lesson_logs_second <- lesson_logs_second %>% dplyr::select(!ends_with("Comments")) %>% dplyr::select(!contains("Files_Id")) %>% dplyr::select(!contains("Files_Type")) %>% dplyr::select(!contains("Files_Size"))  %>% dplyr::select(!contains("Files_Name"))
```





## Creating different dataframes

### Prep time
```{r}
lesson_logs_k_preptime <-lesson_logs_k %>% dplyr::select(ends_with("PrepTime_1"))
names(lesson_logs_k_preptime) <- LessonList
lesson_logs_k_preptime <- cbind(lesson_logs_k_preptime, Teacher = lesson_logs_k$RecipientLastName)
lesson_logs_k_preptime <- lesson_logs_k_preptime %>% pivot_longer(!Teacher, names_to = "Lesson", values_to = "PrepTime") %>% drop_na()
lesson_logs_k_preptime$PrepTime <- as.numeric(as.character(lesson_logs_k_preptime$PrepTime))
lesson_logs_first_preptime <-lesson_logs_first %>% dplyr::select(ends_with("PrepTime_1"))
names(lesson_logs_first_preptime) <- LessonList
lesson_logs_first_preptime <- cbind(lesson_logs_first_preptime, Teacher = lesson_logs_first$RecipientLastName)
lesson_logs_first_preptime <- lesson_logs_first_preptime %>% pivot_longer(!Teacher, names_to = "Lesson", values_to = "PrepTime") %>% drop_na()
lesson_logs_first_preptime$PrepTime <- as.numeric(as.character(lesson_logs_first_preptime$PrepTime))
lesson_logs_second_preptime <-lesson_logs_second %>% dplyr::select(ends_with("PrepTime_1"))
names(lesson_logs_second_preptime) <- LessonList
lesson_logs_second_preptime <- cbind(lesson_logs_second_preptime, Teacher = lesson_logs_second$RecipientLastName)
lesson_logs_second_preptime <- lesson_logs_second_preptime %>% pivot_longer(!Teacher, names_to = "Lesson", values_to = "PrepTime") %>% drop_na()
lesson_logs_second_preptime$PrepTime <- as.numeric(as.character(lesson_logs_second_preptime$PrepTime))
```

### Teaching time
```{r}
lesson_logs_k_teachingtime <-lesson_logs_k %>% dplyr::select(ends_with("TeachingTime_1"))
names(lesson_logs_k_teachingtime ) <- LessonList
lesson_logs_k_teachingtime  <- cbind(lesson_logs_k_teachingtime , Teacher = lesson_logs_k$RecipientLastName)
lesson_logs_k_teachingtime  <- lesson_logs_k_teachingtime  %>% pivot_longer(!Teacher, names_to = "Lesson", values_to = "TeachingTime") %>% drop_na()
lesson_logs_k_teachingtime$TeachingTime <- as.numeric(as.character(lesson_logs_k_teachingtime$TeachingTime))
lesson_logs_first_teachingtime <-lesson_logs_first %>% dplyr::select(ends_with("TeachingTime_1"))
names(lesson_logs_first_teachingtime ) <- LessonList
lesson_logs_first_teachingtime  <- cbind(lesson_logs_first_teachingtime , Teacher = lesson_logs_first$RecipientLastName)
lesson_logs_first_teachingtime  <- lesson_logs_first_teachingtime  %>% pivot_longer(!Teacher, names_to = "Lesson", values_to = "TeachingTime") %>% drop_na()
lesson_logs_first_teachingtime$TeachingTime <- as.numeric(as.character(lesson_logs_first_teachingtime$TeachingTime))
lesson_logs_second_teachingtime <-lesson_logs_second %>% dplyr::select(ends_with("TeachingTime_1"))
names(lesson_logs_second_teachingtime ) <- LessonList
lesson_logs_second_teachingtime  <- cbind(lesson_logs_second_teachingtime , Teacher = lesson_logs_second$RecipientLastName)
lesson_logs_second_teachingtime  <- lesson_logs_second_teachingtime  %>% pivot_longer(!Teacher, names_to = "Lesson", values_to = "TeachingTime") %>% drop_na()
lesson_logs_second_teachingtime$TeachingTime <- as.numeric(as.character(lesson_logs_second_teachingtime$TeachingTime))
```

### Combining dataframes

```{r}
prep_and_teaching_time_k <- cbind(lesson_logs_k_preptime, TeachingTime = lesson_logs_k_teachingtime$TeachingTime)
prep_and_teaching_time_k$Lesson <- factor(prep_and_teaching_time_k$Lesson , levels = LessonList)
prep_and_teaching_time_first <- cbind(lesson_logs_first_preptime, TeachingTime = lesson_logs_first_teachingtime$TeachingTime)
prep_and_teaching_time_first$Lesson <- factor(prep_and_teaching_time_first$Lesson , levels = LessonList)
lesson_logs_second_teachingtime[65,] <- NA
prep_and_teaching_time_second <- cbind(lesson_logs_second_preptime, TeachingTime = lesson_logs_second_teachingtime$TeachingTime)
prep_and_teaching_time_second$Lesson <- factor(prep_and_teaching_time_second$Lesson , levels = LessonList)
```

### Activities

#### By Lessons

```{r}
lesson_logs_k_activities <- lesson_logs_k %>% dplyr::select (Lesson = WhichLesson, contains("Implementation")) %>%  gather(key = Activity, value = Implementation, contains("Implementation")) %>% drop_na()
lesson_logs_k_activities$Implementation <- as.factor(lesson_logs_k_activities$Implementation) 
lesson_logs_first_activities <- lesson_logs_first %>% dplyr::select (Lesson = G1WhichLesson, contains("Implementation")) %>%  gather(key = Activity, value = Implementation, contains("Implementation")) %>% drop_na()
lesson_logs_first_activities$Implementation <- as.factor(lesson_logs_first_activities$Implementation)
lesson_logs_second_activities <- lesson_logs_second %>% dplyr::select (Lesson = WhichLesson, contains("Implementation")) %>%  gather(key = Activity, value = Implementation, contains("Implementation")) %>% drop_na()
lesson_logs_second_activities$Implementation <- as.factor(lesson_logs_second_activities$Implementation)
lesson_logs_k_activities$Implementation <- factor(lesson_logs_k_activities$Implementation, levels = c("AsDescribed", "WithModifications", "NotImplemented"))
lesson_logs_first_activities$Implementation <- factor(lesson_logs_first_activities$Implementation, levels = c("AsDescribed", "WithModifications", "NotImplemented"))
lesson_logs_second_activities$Implementation <- factor(lesson_logs_second_activities$Implementation, levels = c("AsDescribed", "WithModifications", "NotImplemented"))
lesson_logs_k_activities$Activity <- right_side(lesson_logs_k_activities$Activity,1) 
lesson_logs_first_activities$Activity <- right_side(lesson_logs_first_activities$Activity,1) 
lesson_logs_second_activities$Activity <- right_side(lesson_logs_second_activities$Activity,1)
```

#### By Teachers

```{r}
lesson_logs_k_activities_teachers <- lesson_logs_k %>% dplyr::select (Lesson = WhichLesson, contains("Implementation"), RecipientLastName, Grade) %>%  gather(key = Activity, value = Implementation, contains("Implementation")) %>% drop_na()
lesson_logs_k_activities_teachers$Implementation <- as.factor(lesson_logs_k_activities_teachers$Implementation) lesson_logs_first_activities_teachers <- lesson_logs_first %>% dplyr::select (Lesson = G1WhichLesson, contains("Implementation"), RecipientLastName, Grade) %>%  gather(key = Activity, value = Implementation, contains("Implementation")) %>% drop_na()
lesson_logs_first_activities_teachers$Implementation <- as.factor(lesson_logs_first_activities_teachers$Implementation) #make sure it's a factor
lesson_logs_second_activities_teachers <- lesson_logs_second %>% dplyr::select (Lesson = WhichLesson, contains("Implementation"), RecipientLastName, Grade) %>%  gather(key = Activity, value = Implementation, contains("Implementation")) %>% drop_na()
lesson_logs_second_activities_teachers$Implementation <- as.factor(lesson_logs_second_activities_teachers$Implementation) #make sure it's a factor
lesson_logs_activities_teachers <- rbind(lesson_logs_k_activities_teachers, lesson_logs_first_activities_teachers, lesson_logs_second_activities_teachers)
lesson_logs_activities_teachers$Activity <- right_side(lesson_logs_activities_teachers$Activity,1)
```

# Visualizations & Descriptives

## Preparation time

### Kindergarten

```{r}
preptime_k_bar <- ggplot(prep_and_teaching_time_k, aes(x = Lesson, y =  PrepTime)) +
  geom_bar(stat = "summary", fun.y = "mean")+
  theme_bw()
preptime_k_bar
min_max_mean_sd(prep_and_teaching_time_k$PrepTime)
```

### First Grade

```{r}
preptime_first_bar <- ggplot(prep_and_teaching_time_first, aes(x = Lesson, y =  PrepTime)) +
  geom_bar(stat = "summary", fun.y = "mean")+
  theme_bw()
preptime_first_bar
min_max_mean_sd(prep_and_teaching_time_first$PrepTime)
```

### Second Grade

```{r}
preptime_second_bar <- ggplot(prep_and_teaching_time_second, aes(x = Lesson, y =  PrepTime)) +
  geom_bar(stat = "summary", fun.y = "mean")+
  theme_bw()
preptime_second_bar
min_max_mean_sd(prep_and_teaching_time_second$PrepTime)
```

## Teaching time

### Kindergarten

```{r}
teachingtime_k_bar <- ggplot(prep_and_teaching_time_k, aes(x = Lesson, y =  TeachingTime)) +
  geom_bar(stat = "summary", fun.y = "mean")+
  theme_bw()
teachingtime_k_bar
min_max_mean_sd(prep_and_teaching_time_k$TeachingTime)
```

### First Grade
```{r}
teachingtime_first_bar <- ggplot(prep_and_teaching_time_first, aes(x = Lesson, y =  TeachingTime)) +
  geom_bar(stat = "summary", fun.y = "mean")+
  theme_bw()
teachingtime_first_bar
```

```{r}
min_max_mean_sd(prep_and_teaching_time_first$TeachingTime)
```

### Second Grade

```{r}
teachingtime_second_bar <- ggplot(prep_and_teaching_time_second, aes(x = Lesson, y =  TeachingTime)) +
  geom_bar(stat = "summary", fun.y = "mean")+
  theme_bw()
teachingtime_second_bar
min_max_mean_sd(prep_and_teaching_time_secibd$TeachingTime)
```


## Activities

```{r}
activity_implementation <- lesson_logs_activities_teachers %>% group_by(Grade,Lesson,Activity) %>% dplyr::mutate(NumberOfEntries=n()) %>% group_by(Grade, Lesson, Activity, Implementation) %>% dplyr::mutate(TypeHowOften=n()) %>% dplyr::mutate(Proportion = TypeHowOften/NumberOfEntries) %>% group_by(Grade, Lesson, Activity, Implementation, Proportion) %>% unique %>% as.data.frame()
activity_implementation$Activity <- as.factor(activity_implementation$Activity)
activity_implementation <- activity_implementation %>% dplyr::select(-RecipientLastName, -NumberOfEntries, -TypeHowOften) %>% unique()
activity_implementation$Implementation <- factor(activity_implementation$Implementation, levels = c("AsDescribed", "WithModifications", "NotImplemented"))
```

```{r}
activity_implementation_table <- table (lesson_logs_activities$Activity, lesson_logs_activities$Implementation)
```

### Kindergarten
```{r}
activities_bar_k <- ggplot(activity_implementation[activity_implementation$Grade=="Kindergarten",], aes(Activity, Proportion, fill = Implementation)) +
          geom_bar(stat = "identity", position = "stack") + 
          theme_bw()+
          facet_wrap(~Lesson, ncol = 4)
activities_bar_k
```

### First Grade
```{r}
activities_bar_first <- ggplot(activity_implementation[activity_implementation$Grade=="FirstGrade",], aes(Activity, Proportion, fill = Implementation)) +
          geom_bar(stat = "identity", position = "stack") + 
          theme_bw()+
          facet_wrap(~Lesson, ncol = 4)
activities_bar_first
activity_implementation_first <- lesson_logs_activities_teachers %>%  filter(Grade=="FirstGrade") %>% dplyr::select(Implementation) %>% mutate(OverallN = n()) %>%
   group_by(Implementation)  %>%
  mutate(N = n()) %>% ungroup() %>% unique() %>%
  mutate(Proportion =  N/OverallN)
activity_implementation_first 
```

### Second Grade
```{r}
activities_bar_second <- ggplot(activity_implementation[activity_implementation$Grade=="SecondGrade",], aes(Activity, Proportion, fill = Implementation)) +
          geom_bar(stat = "identity", position = "stack") + 
          theme_bw()+
          facet_wrap(~Lesson, ncol = 4)
activities_bar_second
activity_implementation_second <- lesson_logs_activities_teachers %>%  filter(Grade=="SecondGrade") %>% dplyr::select(Implementation) %>% mutate(OverallN = n()) %>%
   group_by(Implementation)  %>%
  mutate(N = n()) %>% ungroup() %>% unique() %>%
  mutate(Proportion =  N/OverallN)
activity_implementation_second
```

# FOI per teacher

```{r}
activity_implementation_teachers <- lesson_logs_activities_teachers %>% dplyr::select(RecipientLastName, Implementation) %>% group_by(RecipientLastName) %>% mutate(OverallN = n()) %>%
   group_by(RecipientLastName, Implementation)  %>%
  mutate(N = n()) %>% ungroup() %>% unique() %>%
  mutate(Proportion =  N/OverallN) %>% arrange(RecipientLastName)
activity_implementation_teachers$Implementation <- factor(activity_implementation_teachers$Implementation, levels = c("AsDescribed", "WithModifications", "NotImplemented"))
activity_implementation_teachers 
FOI_teachers <- activity_implementation_teachers %>% filter(!Implementation=="NotImplemented") %>% group_by(RecipientLastName) %>% dplyr::select(RecipientLastName, Implementation, Proportion) %>% mutate(Implemented = sum(Proportion)) %>% select (RecipientLastName, Implemented) %>% unique()
write.csv(FOI_teachers, "210606_FOI_Teachers.csv", row.names = F)
activities_bar_teachers <- ggplot(activity_implementation_teachers, aes(RecipientLastName, Proportion, fill = Implementation)) +
          geom_bar(stat = "identity", position = "stack") + 
          theme_bw()
activities_bar_teachers
```



