---
title: "CAL ScratchJr CSA pre/post analysis"
author: "L E de Ruiter"
date: "6/04/2021"
output: html_document
---


# Preliminaries
## About the data

The current data contains responses from students before they were taught the CAL curriculum and after they were taught the CAL curriculum as well as teachers before they attended the professional development (PD) and after. 

## Load libraries

```{r}
checkpoint::checkpoint("2021-06-10")
```

## Colorblind-friendly palette

```{r colour_palettes, include=FALSE}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
cbbPalette <- c("#999999","#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7","#5C5C5C")
```


## Read in data
```{r}
CSA <- read.csv("210603_CSA_clean.csv", strip.white = T, stringsAsFactors = T, na.strings = c("", NA))
CSA <- CSA %>% slice(-1:-2) 
```


```{r}
CSA <- gdata::drop.levels(CSA)
```


```{r}
teacher_info <- read.csv("210606_Teacher_Info_FOI.csv", strip.white = T, stringsAsFactors = T, na.strings = c("", NA))
```

```{r}
student_info <- read.csv("210610_DoE_Pilot_Student_Info.csv", strip.white = T, stringsAsFactors = T, na.strings = c("", NA))
```

Data from the Shaffer Group. 
```{r}
shaffer <-read.csv("210603_CSA_Shaffer_clean.csv", strip.white = T, stringsAsFactors = T, na.strings = c("", NA))
shaffer <- shaffer %>% slice(-1:-2)
```


## Functions

### Mode

```{r}
# Create the function.
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
```


### Min, max, mean, SD

```{r}
min_max_mean_sd <- function(variable){
  
  min = round(min(variable, na.rm = T),1)
  max = round(max(variable, na.rm = T),1)
  mean = round(mean(variable, na.rm = T),1)
  sd = round(sd(variable, na.rm = T),1)
  
  my_list = list(min, max, mean, sd) 
  
  return(my_list)
}
```

```{r}
#+++++++++++++++++++++++++
# Function to calculate the mean and the standard deviation
  # for each group
#+++++++++++++++++++++++++
data_summary <- function(data, varname, groupnames){
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
 return(data_sum)
}
```


## Vectors

### Teachers

These are teachers who taught the curriculum
```{r}
FinalTeachers <- c("T01", "T02", "T03", "T04", "T05") 
```


# Cleaning data

## Remove IRR
We're only interested in the primary researcher data

```{r}
CSA <- CSA %>% filter(IRR != "IRR" | is.na(IRR)) 
```

```{r}
shaffer <- shaffer %>% filter(IRR != "IRR" | is.na(IRR))
```


## Fixing SC -> string variable names

```{r}
CSA$SC0 <- as.numeric(as.character(CSA$SC0))
CSA$SC1 <- as.numeric(as.character(CSA$SC1))
CSA$SC2 <- as.numeric(as.character(CSA$SC2))
CSA$SC3 <- as.numeric(as.character(CSA$SC3))
CSA$SC4 <- as.numeric(as.character(CSA$SC4))
CSA$SC5 <- as.numeric(as.character(CSA$SC5))
```

```{r}
shaffer$SC0 <- as.numeric(as.character(shaffer$SC0))
shaffer$SC1 <- as.numeric(as.character(shaffer$SC1))
shaffer$SC2 <- as.numeric(as.character(shaffer$SC2))
shaffer$SC3 <- as.numeric(as.character(shaffer$SC3))
shaffer$SC4 <- as.numeric(as.character(shaffer$SC4))
shaffer$SC5 <- as.numeric(as.character(shaffer$SC5))
```


```{r}
CSA$EmergentScore <- as.numeric(as.character(CSA$EmergentScore))
CSA$CodingDecodingScore <- as.numeric(as.character(CSA$CodingDecodingScore))
CSA$FluencyScore <- as.numeric(as.character(CSA$FluencyScore))
CSA$NewKnowledgeScore <- as.numeric(as.character(CSA$NewKnowledgeScore))
CSA$PurposefulnessScore <- as.numeric(as.character(CSA$PurposefulnessScore))
```


```{r}
shaffer$EmergentScore <- as.numeric(as.character(shaffer$Emergent.Score))
shaffer$CodingDecodingScore <- as.numeric(as.character(shaffer$Coding.and.Decoding.Score))
shaffer$FluencyScore <- as.numeric(as.character(shaffer$Fluency.Score))
shaffer$NewKnowledgeScore <- as.numeric(as.character(shaffer$New.Knowledge.Score))
shaffer$PurposefulnessScore <- NA 
```

Now we can merge the variables 
```{r}
CSA$EmergentScore <- ifelse(is.na(CSA$EmergentScore), CSA$SC1, CSA$EmergentScore)
CSA$CodingDecodingScore <- ifelse(is.na(CSA$CodingDecodingScore), CSA$SC2, CSA$CodingDecodingScore)
CSA$FluencyScore <- ifelse(is.na(CSA$FluencyScore), CSA$SC3, CSA$FluencyScore)
CSA$NewKnowledgeScore <- ifelse(is.na(CSA$NewKnowledgeScore), CSA$SC4, CSA$NewKnowledgeScore)
CSA$PurposefulnessScore <- ifelse(is.na(CSA$PurposefulnessScore), CSA$SC5, CSA$PurposefulnessScore)
```

```{r}
shaffer$EmergentScore <- ifelse(is.na(shaffer$EmergentScore), shaffer$SC1, shaffer$EmergentScore)
shaffer$CodingDecodingScore <- ifelse(is.na(shaffer$CodingDecodingScore), shaffer$SC2, shaffer$CodingDecodingScore)
shaffer$FluencyScore <- ifelse(is.na(shaffer$FluencyScore), shaffer$SC3, shaffer$FluencyScore)
shaffer$NewKnowledgeScore <- ifelse(is.na(shaffer$NewKnowledgeScore), shaffer$SC4, shaffer$NewKnowledgeScore)
shaffer$PurposefulnessScore <- ifelse(is.na(shaffer$PurposefulnessScore), shaffer$SC5, shaffer$PurposefulnessScore)
```

Calculating TotalScore
```{r}
for (row in 1:nrow(CSA)){
  
  CSA$TotalScore[row] <- sum(CSA$EmergentScore[row], CSA$CodingDecodingScore[row], CSA$FluencyScore[row], CSA$NewKnowledgeScore[row], CSA$PurposefulnessScore[row])
  
}

```

```{r}
for (row in 1:nrow(shaffer)){
  
  shaffer$TotalScore[row] <- sum(shaffer$EmergentScore[row], shaffer$CodingDecodingScore[row], shaffer$FluencyScore[row], shaffer$NewKnowledgeScore[row], shaffer$PurposefulnessScore[row])
  
}

```

We now can remove the variables SC0...SC5 

```{r}
CSA$SC0 <- NULL
CSA$SC1 <- NULL
CSA$SC2 <- NULL
CSA$SC3 <- NULL
CSA$SC4 <- NULL
CSA$SC5 <- NULL
```

```{r}
shaffer$SC0 <- NULL
shaffer$SC1 <- NULL
shaffer$SC2 <- NULL
shaffer$SC3 <- NULL
shaffer$SC4 <- NULL
shaffer$SC5 <- NULL
```

We can also remove the superfluous variables

```{r}
shaffer$Emergent.Score <- NULL
shaffer$Coding.and.Decoding.Score <- NULL
shaffer$Fluency.Score <- NULL
shaffer$New.Knowledge.Score <- NULL
```


We are also removing CodingStage

```{r}
CSA$CodingStage <- NULL
```

```{r}
shaffer$Coding.Stage <- NULL
```

## Adding TeacherID

```{r}
teacher_info <- teacher_info %>% dplyr::select(TeacherName, TeacherID)
```

```{r}
CSA <- merge(CSA, teacher_info, by.x="LastName", by.y="TeacherName", all.x=TRUE)
```

## Adding Student Info

```{r}
student_info <- student_info %>% dplyr::select(StudentID, Gender, TeacherID)
CSA  <- merge(CSA, student_info, by.x="StudentID", by.y="StudentID", all.x=TRUE)
```

```{r}
shaffer <- merge(shaffer, student_info, by.x="StudentID", by.y="StudentID", all.x=TRUE)
```

We now have several columns repeated and complementary (TeacherID.x, and TeacherID.y). 
```{r}
CSA <- CSA  %>% dplyr::mutate(TeacherID = coalesce(TeacherID.x,TeacherID.y))
```

## Selecting variables

Removing variables
```{r}
CSA <- CSA %>% dplyr::select(-CaseNumber, -EndDate, -Status, -IPAddress, -Progress, -Finished, -RecordedDate, -ResponseId, -RecipientFirstName, -RecipientLastName, -RecipientEmail, -ExternalReference, -LocationLatitude, -LocationLongitude, -DistributionChannel, -UserLanguage, -Administrator, -IRR) %>% dplyr::select(-FirstName, -LastName, -TeacherID.x, TeacherID.y) %>%  dplyr::select(!ends_with("Comments")) 
```

```{r}
shaffer <- shaffer %>% dplyr::select(-EndDate, -Status, -IPAddress, -Progress, -Finished, -RecordedDate, -ResponseId,-RecipientFirstName, -RecipientLastName, -RecipientEmail, -ExternalReference, -LocationLatitude, -LocationLongitude, -DistributionChannel, -UserLanguage, -DateofBirth, -Gender.x, -Researcher, -IRR) %>% dplyr::select(!ends_with("Comments")) %>% dplyr::rename(Gender = Gender.y)
```

## Renaming variables
```{r}
CSA <- CSA %>% dplyr::rename (DateTime = StartDate, DurationSeconds = Duration..in.seconds., TimeOfTest = TestTimePoint)
```

```{r}
shaffer <- shaffer %>% dplyr::rename (DateTime = StartDate, DurationSeconds = Duration..in.seconds., TimeOfTest = TestTimePoint)
```


## Reordering variables

```{r}
CSA <- CSA %>% dplyr::select(StudentID, TeacherID, Gender, DateTime:EmergentScore, CodingDecodingScore, FluencyScore, NewKnowledgeScore, PurposefulnessScore, TotalScore)
```

```{r}
shaffer <- shaffer %>% dplyr::select(StudentID, TeacherID, Gender, DateTime:EmergentScore, CodingDecodingScore, FluencyScore, NewKnowledgeScore, PurposefulnessScore, TotalScore)
```

## Merging datasets

```{r}
CSA <- rbind(CSA, shaffer)
```

Comment in this discussion suggests there's a way to do this for the entire data frame instead of for isolated variables using the drop.levels function in the gdata package.


```{r}
CSA <- gdata::drop.levels(CSA)
```


## Recoding factors and factor levels
```{r}
CSA$Grade <- factor(CSA$Grade, levels = c("Kindergarten", "FirstGrade", "SecondGrade"))
```

We will create a new variable that uses the initial of the first name and the last name to form "name".

```{r}
CSA$TimeOfTest <- as.factor(CSA$TimeOfTest) 

```

## Fixing the date
We need to get the date.
```{r}
CSA$DateTime <- as.character(CSA$DateTime) 
CSA$DateTime  <- CSA$DateTime  %>%
    strsplit(., " ") %>% 
    sapply(head, 1 ) 

CSA$DateTime <- mdy(CSA$DateTime)
```


Recall that on 12/23, questions 2.1 and 2.2 were swapped. 

```{r}
# 
CSA$Q2.1_new <- ifelse(CSA$DateTime < "2020-12-23", CSA$Q2.2,  CSA$Q2.1) 
CSA$Q2.2_new <- ifelse(CSA$DateTime >= "2020-12-23", CSA$Q2.1,  CSA$Q2.2) 

CSA$Q2.1 <- CSA$Q2.1_new
CSA$Q2.2 <- CSA$Q2.2_new

CSA$Q2.1_new <- NULL
CSA$Q2.2_new <- NULL
```


## Calculating new variables

### Coding Stages

```{r}
CSA[, 11:40][is.na(CSA[, 11:40])] <- 0
```

Create a variable CodingStage
```{r}
CSA$CodingStage = NA
```

```{r}

for (row in 1:nrow(CSA)){ 
  if (CSA[row, "PurposefulnessScore"] >= 5){
  CodingStage = "Purposefulness"
  
 } else if (CSA[row, "NewKnowledgeScore"] >= 5){
  CodingStage = "NewKnowledge"

} else if (CSA[row,"NewKnowledgeScore"] &  CSA[row,"NewKnowledgeScore"] < 5 & CSA[row,"FluencyScore"] >= 5){
  CodingStage = "Fluency"
  
} else if (CSA[row,"FluencyScore"] &  CSA[row,"FluencyScore"] < 5 & CSA[row,"CodingDecodingScore"] >= 5){
  CodingStage = "CodingDecoding" 
  
 }else if (CSA[row,"EmergentScore"] & CSA[row,"EmergentScore"] >= 4){
     CodingStage = "Emergent"  
     
} else {
  CodingStage = "Pre Coding Stage"
}
  
  CSA$CodingStage[row] <- CodingStage
  
}
```

```{r}
CSA$CodingStage <- factor(CSA$CodingStage, levels = c("Pre Coding Stage", "Emergent","CodingDecoding","Fluency","NewKnowledge", "Purposefulness")) 
```


### Weighted Score

```{r Weighting}
for (row in 1:nrow(CSA)){ 
  CSA$WeightedScore[row] <- sum(CSA$Emergent[row]*1.1, CSA$CodingDecoding[row]*1.2, CSA$Fluency[row]*1.3, CSA$NewKnowledge[row]*(1.4),CSA$NewKnowledge[row]*(1.5) )
  
}

```

```{r}
number_of_stages <- 5

max_sum_score <- number_of_stages * 6
weighted_score_max <- 6  * 1.1  + 6  * 1.2 + 6  * 1.3 + 6  * 1.4 + 6 * 1.5 

```



## Creating additional data frames

### Students only

```{r}
CSA_students <- subset (CSA, StudentOrTeacher == "Student")
```

```{r}
CSA_students$TimeOfTest <- factor(CSA_students$TimeOfTest, levels = c("PreCurriculum", "PostCurriculum"))
```

```{r}
CSA_students_wide <- CSA_students %>% dplyr::select(StudentID, School, Grade, TimeOfTest, WeightedScore)%>% dplyr::mutate(row = row_number())
```

```{r}
CSA_students_wide <- CSA_students_wide  %>%  pivot_wider(
    names_from = TimeOfTest, 
    values_from = WeightedScore) %>% dplyr::select(-row) %>% arrange(StudentID)
CSA_students_wide
```

```{r}
CSA_students_wide_precurriculum <- CSA_students_wide %>% dplyr::select(-PostCurriculum) %>% na.omit()
CSA_students_wide_postcurriculum <- CSA_students_wide%>% dplyr::select(-PreCurriculum) %>% na.omit()
```

```{r}
CSA_students_wide <- left_join(CSA_students_wide_precurriculum, CSA_students_wide_postcurriculum, by = c("StudentID", "School", "Grade")) %>% dplyr::select(StudentID, School, Grade, PreCurriculum, PostCurriculum)
```

```{r}
CSA_students_wide$ChangeScore <- CSA_students_wide$PostCurriculum - CSA_students_wide$PreCurriculum
```

### Teachers only

```{r}
CSA_teachers <- subset (CSA, StudentOrTeacher == "Teacher")
```
Let's use teachers who taught.

```{r}
CSA_teachers <- CSA_teachers %>% dplyr::filter(TeacherID %in% FinalTeachers) %>% dplyr::select(TeacherID, School, TimeOfTest, WeightedScore, CodingStage) %>% dplyr::mutate(row = row_number()) %>% dplyr::mutate(TeacherID2 = paste0(School, TeacherID))
```


```{r}
CSA_teachers$TimeOfTest <- factor(CSA_teachers$TimeOfTest, levels = c("PreTraining", "PostTraining", "PostCurriculumTeacher"))
```


```{r}
CSA_teachers_wide <- CSA_teachers %>% dplyr::select(-TeacherID, -School) %>% pivot_wider(
    names_from = TimeOfTest, 
    values_from = WeightedScore) %>% dplyr::select(-row) %>% arrange(TeacherID2) 
```


```{r}
CSA_teachers_wide_pre <- CSA_teachers_wide %>% dplyr::select(PreTraining, TeacherID2) %>% na.omit()
CSA_teachers_wide_post <-CSA_teachers_wide %>% dplyr::select(PostTraining, TeacherID2) %>% na.omit()
CSA_teachers_wide_postcurriculum <- CSA_teachers_wide %>% dplyr::select(PostCurriculumTeacher, TeacherID2) %>% na.omit()
```

```{r}
CSA_teachers_wide <- merge(CSA_teachers_wide_pre, CSA_teachers_wide_post, by.x = "TeacherID2", by.y = "TeacherID2")
CSA_teachers_wide < cbind(CSA_teachers_wide, CSA_teachers_wide_postcurriculum, by = "TeacherID2", all = T)
```

```{r}
merge(data.frame(CSA_teachers_wide, row.names=NULL), data.frame( CSA_teachers_wide_postcurriculum, row.names=NULL), 
  by = 0, all = TRUE)[-1]
```


```{r}
CSA_teachers_wide %>% dplyr::select(TeacherID2)
```


```{r}
CSA_teachers_wide$ChangeScore1 <- (CSA_teachers_wide$PostTraining-CSA_teachers_wide$PreTraining)
```



### Small df
```{r}
CSA_small <- CSA %>% dplyr::select(StudentID, TimeOfTest, WeightedScore, CodingStage)
```


# Visualizations


## Barplot weighted Score

```{r}
CSA_summary_students <- data_summary(CSA_students, varname="WeightedScore",  groupnames="TimeOfTest")
CSA_summary_students$TimeOfTest <- factor(CSA_summary_students$TimeOfTest, levels = c("PreCurriculum", "PostCurriculum"))
CSA_summary_students <-na.omit(CSA_summary_students) 

CSA_summary_teachers  <- data_summary(CSA_teachers, varname="WeightedScore", groupnames="TimeOfTest")
CSA_summary_teachers$TimeOfTest <- factor(CSA_summary_teachers$TimeOfTest, levels = c("PreTraining", "PostTraining", "PostCurriculumTeacher"))
```

```{r}
PrePost_WeightedScore_CSA_students <- ggplot(CSA_summary_students , aes(TimeOfTest, WeightedScore, fill = TimeOfTest))+
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge")+
  geom_errorbar(aes(ymin=WeightedScore-sd, ymax=WeightedScore+sd), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values=cbPalette)+
  theme_bw()+
  xlab ("Time of Test")+
  ylab ("CSA Score")

ggsave("PrePost_WeightedScore_CSA.png")
```
```{r}
PrePost_WeightedScore_CSA_students_grade_barplot <- ggplot(CSA_students[!is.na(CSA_students$Grade),], aes(TimeOfTest, WeightedScore, fill = TimeOfTest))+
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge")+
  #geom_errorbar(aes(ymin=WeightedScore-sd, ymax=WeightedScore+sd), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values=cbPalette)+
  theme_bw()+
  xlab ("Time of Test")+
  ylab ("CSA Weighted Score")+
  facet_wrap(~Grade)+
  theme(legend.position = "none")
ggsave("PrePost_WeightedScore_CSA_students_barplot.png")
```

## Boxplot weighted

```{r}
PrePost_WeightedScore_CSA_students_grade_boxplot <- ggplot(CSA_students[!is.na(CSA_students$Grade),], aes(TimeOfTest, WeightedScore, fill = TimeOfTest))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  theme_bw()+
  xlab ("Time of Test")+
  ylab ("CSA Weighted Score")+
  facet_wrap(~Grade)+
  theme(legend.position = "none")
ggsave("PrePost_WeightedScore_CSA_students_box.png")
```

```{r}
PrePost_WeightedScore_CSA_teachers <- ggplot(CSA_summary_teachers , aes(TimeOfTest, WeightedScore, fill = TimeOfTest))+
  geom_bar(stat = "summary", fun.y = "mean", position = "dodge")+
  geom_errorbar(aes(ymin=WeightedScore-sd, ymax=WeightedScore+sd), width=.2, position=position_dodge(.9)) +
  scale_fill_manual(values=cbPalette)+
  theme_bw()+
  xlab ("Time of Test")+
  ylab ("CSA Score")
ggsave("PrePost_WeightedScore_CSA_teachers.png")
```

## Pirateplot weighted score

```{r}
CSA_pirate <- yarrr::pirateplot(formula = WeightedScore ~ TimeOfTest, 
                   data = CSA_students,
                   theme = 2,
                   point.o = .4,
                   bean.b.o = .3,
                   pal = 'info') 
CSA_pirate
```
## Barplot stages

```{r}
CSA_Stage_bar <- ggplot(CSA_students, aes(CodingStage, group = TimeOfTest, fill=TimeOfTest))+
  geom_bar(stat = "count", position = "dodge")+
  scale_fill_manual(values=cbPalette)+
  scale_x_discrete(drop = FALSE)+
  theme_minimal()+theme_classic()+theme(legend.position="top")+
  facet_wrap(~TimeOfTest)+
  theme_bw()+
  xlab("Coding Stage")+
  ylab("Number of Participants")+
  ylim(0,200)+
  geom_text(stat='count', aes(label=..count..), vjust=-1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position = "none")
ggsave("CSA_students_stage_bar.png")
```
```{r}
CSA_Stage_bar_teachers <- ggplot(CSA_teachers, aes(CodingStage, group = TimeOfTest, fill=TimeOfTest))+
  geom_bar(stat = "count", position = "dodge")+
  scale_fill_manual(values=cbPalette)+
  scale_x_discrete(drop = FALSE)+
  theme_minimal()+theme_classic()+theme(legend.position="top")+
  facet_wrap(~TimeOfTest)+
  theme_bw()+
  xlab("Coding Stage")+
  ylab("Number of Participants")+
  ylim(0,6)+
  geom_text(stat='count', aes(label=..count..), vjust=-1)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  theme(legend.position = "none")
ggsave("Teacher_CSA_Stage_bar.png")
```

## Barplot change score

```{r}
CSA_bar_changescore_students <- ggplot(CSA_students_wide, aes(x = Grade, y = ChangeScore, fill = Grade))+
  geom_boxplot()+
  scale_fill_manual(values=cbPalette)+
  scale_x_discrete(drop = FALSE)+
  theme_minimal()+theme_classic()+theme(legend.position="top")+
  theme_bw()+
  xlab("Grade")+
  ylab("Change score")+
  theme(legend.position = "none")
ggsave("210610_boxplot_CSA_changescore.png")
```



# Descriptives and Analyses

## Average change score

### Students
```{r}
min_max_mean_sd(CSA_students_wide$ChangeScore[CSA_students_wide$Grade =="Kindergarten"])
min_max_mean_sd(CSA_students_wide$ChangeScore[CSA_students_wide$Grade =="FirstGrade"])
min_max_mean_sd(CSA_students_wide$ChangeScore[CSA_students_wide$Grade =="SecondGrade"])
```

### Teachers
```{r}
min_max_mean_sd(CSA_teachers_wide$ChangeScore[CSA_teachers_wide$TimeOfTest =="Kindergarten"])
min_max_mean_sd(CSA_teachers_wide$ChangeScore[CSA_teachers_wide$Grade =="FirstGrade"])
min_max_mean_sd(CSA_teacgers_wide$ChangeScore[CSA_teachers_wide$Grade =="SecondGrade"])
```


